---
title: "EDA_20210926"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages

```{r packages, echo=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(corrplot)
library(RColorBrewer)
library(stringr)
```

## Loading Dataset

```{r dataset, echo=FALSE}
movies <- read_tsv("all_top_rated_movies_2021-09-01.tsv")
```

## Data Cleaning 
```{r dataset cleaning}
str(movies)
summary(movies)
glimpse(movies)
```

## Missing Values 
```{r missing}
colSums(is.na(movies))
# 16 missing values in overview and 2 in genre_ids 
# Removing them 
movies = na.omit(movies)
colSums(is.na(movies))
```

## Duplicated rows 
```{r duplicates}
length(unique(movies$title))
# Returns the unique rows in movies dataset
movies %>% distinct()
# Remove duplicate rows based on multiple variables 
movies %>% distinct(title, release_date, .keep_all = TRUE)
# Number of rows removed 
length(unique(movies$title))
```

## Explanatory Data Analysis EDA 
```{r intro}
# First few rows of movies dataset 
head(movies)
# Last few rows of movies dataset 
tail(movies)
# Summary Statistics 
summary(movies)
```

# Top 20 popular movies 
```{r popularity}
top_20_movies <- head(movies[order(movies$popularity, decreasing = TRUE), c("title", "popularity")], n = 20)
top_20_movies$title <- reorder(top_20_movies$title, as.numeric(top_20_movies$popularity))
ggplot(top_20_movies, aes(title, popularity)) +
  geom_col(position = "dodge", aes(fill = popularity)) +
  coord_flip() +
  labs(x = "Movie Name",
       y = "Popularity",
       title = "The Most Popular 20 Movies") +
  scale_fill_gradient(low = "gold", high = "purple")
```

# Highest Protfitable Movies
```{r revenue}
highest_profit_movies <- head(movies[order(movies$revenue, decreasing = TRUE), c("title", "revenue")], n = 20)
highest_profit_movies$title <- reorder(highest_profit_movies$title, as.numeric(highest_profit_movies$revenue))
ggplot(highest_profit_movies, aes(title, revenue)) +
  geom_col(position = "dodge", aes(fill = revenue)) +
  coord_flip() +
  labs(x = "Movie Name",
       y = "Revenue",
       title = "20 Highest Profitable Movies") +
  scale_fill_gradient(low = "gold", high = "purple")
```

# 20 Highest Budget Movies 
```{r budget}
highest_budget_movies <- head(movies[order(movies$budget, decreasing = TRUE), c("title", "budget")], n = 20)
highest_budget_movies$title <- reorder(highest_budget_movies$title, as.numeric(highest_budget_movies$budget))
ggplot(highest_budget_movies, aes(title, budget)) +
  geom_col(position = "dodge", aes(fill = budget)) +
  coord_flip() +
  labs(x = "Movie Name",
       y = "Budget",
       title = "20 Highest Budget Movies") +
  scale_fill_gradient(low = "gold", high = "purple")
```

# The Relative Frequencies of Genres
```{r genres}
action <- ggplot(movies, aes(x = Action)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

adventure <- ggplot(movies, aes(x = Adventure)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

animation <- ggplot(movies, aes(x = Animation)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

comedy <- ggplot(movies, aes(x = Comedy)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

#Plot 1 
ggarrange(action, adventure, animation, comedy + rremove("x.text"),
          ncol = 2, nrow = 2)


crime <- ggplot(movies, aes(x = Crime)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

documentary <- ggplot(movies, aes(x = Documentary)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

drama <- ggplot(movies, aes(x = Drama)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

family <- ggplot(movies, aes(x = Family)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

# Plot 2 
ggarrange(crime, documentary, drama, family + rremove("x.text"),
          ncol = 2, nrow = 2)

fantasy <- ggplot(movies, aes(x = Fantasy)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

history <- ggplot(movies, aes(x = History)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

horror <- ggplot(movies, aes(x = Horror)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

music <- ggplot(movies, aes(x = Music)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

# Plot 3 
ggarrange(fantasy, history, horror, music + rremove("x.text"),
          ncol = 2, nrow = 2)

mystery <- ggplot(movies, aes(x = Mystery)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

romance <- ggplot(movies, aes(x = Romance)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

sciencefiction <- ggplot(movies, aes(x = `Science Fiction`)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

tvmovie <- ggplot(movies, aes(x = `TV Movie`)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

# Plot 4 
ggarrange(mystery, romance, sciencefiction, tvmovie + rremove("x.text"),
          ncol = 2, nrow = 2)

thriller <- ggplot(movies, aes(x = Thriller)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

war <- ggplot(movies, aes(x = War)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "gold") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

western <- ggplot(movies, aes(x = Western)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..)),
                y = (..count..)/sum(..count..)), stat = "count", vjust = -.5) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Relative Frequencies")

# Plot 5 
ggarrange(thriller, war, western + rremove("x.text"),
          ncol = 2, nrow = 2)
```

# Top 20 movies with the longest runtime 
```{r runtime}
longest_runtime_movies <- head(movies[order(movies$runtime, decreasing = TRUE), c("title", "runtime")], n = 20)
longest_runtime_movies$title <- reorder(longest_runtime_movies$title, as.numeric(longest_runtime_movies$runtime))
ggplot(longest_runtime_movies, aes(title, runtime)) +
  geom_col(position = "dodge", aes(fill = runtime)) +
  coord_flip() +
  labs(x = "Movie Name",
       y = "Runtime in Minutes",
       title = "Top 20 Movies with Longest Runtime") +
  scale_fill_gradient(low = "gold", high = "purple")
```

# Vote Averages against Genres
```{r vote genres}
action_vote_average <- movies %>%
  select(c('Action', 'vote_average')) %>%
  filter(Action == "TRUE")
action_vote_average$Action <- str_replace(action_vote_average$Action, "TRUE", "Action")

adventure_vote_average <- movies %>%
  select(c('Adventure', 'vote_average')) %>%
  filter(Adventure == "TRUE")
adventure_vote_average$Adventure <- str_replace(adventure_vote_average$Adventure, "TRUE", "Adventure")

animation_vote_average <- movies %>%
  select(c('Animation', 'vote_average')) %>%
  filter(Animation == "TRUE")
animation_vote_average$Animation <- str_replace(animation_vote_average$Animation, "TRUE", "Animation")

comedy_vote_average <- movies %>%
  select(c('Comedy', 'vote_average')) %>%
  filter(Comedy == "TRUE")
comedy_vote_average$Comedy <- str_replace(comedy_vote_average$Comedy, "TRUE", "Comedy")

crime_vote_average <- movies %>%
  select(c('Crime', 'vote_average')) %>%
  filter(Crime == "TRUE")
crime_vote_average$Crime <- str_replace(crime_vote_average$Crime, "TRUE", "Crime")

drama_vote_average <- movies %>%
  select(c('Drama', 'vote_average')) %>%
  filter(Drama == "TRUE")
drama_vote_average$Drama <- str_replace(drama_vote_average$Drama, "TRUE", "Drama")

family_vote_average <- movies %>%
  select(c('Family', 'vote_average')) %>%
  filter(Family == "TRUE")
family_vote_average$Family <- str_replace(family_vote_average$Family, "TRUE", "Family")

fantasy_vote_average <- movies %>%
  select(c('Fantasy', 'vote_average')) %>%
  filter(Fantasy == "TRUE")
fantasy_vote_average$Fantasy <- str_replace(fantasy_vote_average$Fantasy, "TRUE", "Fantasy")

mystery_vote_average <- movies %>%
  select(c('Mystery', 'vote_average')) %>%
  filter(Mystery == "TRUE")
mystery_vote_average$Mystery <- str_replace(mystery_vote_average$Mystery, "TRUE", "Mystery")

sciencefiction_vote_average <- movies %>%
  select(c('Science Fiction', 'vote_average')) %>%
  filter(`Science Fiction` == "TRUE")
sciencefiction_vote_average$`Science Fiction` <- str_replace(sciencefiction_vote_average$`Science Fiction`, "TRUE", "Science Fiction")

romance_vote_average <- movies %>%
  select(c('Romance', 'vote_average')) %>%
  filter(Romance == "TRUE") 
romance_vote_average$Romance <- str_replace(romance_vote_average$Romance, "TRUE", "Romance")

tvmovie_vote_average <- movies %>%
  select(c('TV Movie', 'vote_average')) %>%
  filter(`TV Movie` == "TRUE") 
tvmovie_vote_average$`TV Movie` <- str_replace(tvmovie_vote_average$`TV Movie`, "TRUE", "TV Movie")

thriller_vote_average <- movies %>%
  select(c('Thriller', 'vote_average')) %>%
  filter(Thriller == "TRUE") 
thriller_vote_average$Thriller <- str_replace(thriller_vote_average$Thriller, "TRUE", "Thriller")

war_vote_average <- movies %>%
  select(c('War', 'vote_average')) %>%
  filter(War == "TRUE") 
war_vote_average$War <- str_replace(war_vote_average$War, "TRUE", "War")

western_vote_average <- movies %>%
  select(c('Western', 'vote_average')) %>%
  filter(Western == "TRUE") 
western_vote_average$Western <- str_replace(western_vote_average$Western, "TRUE", "Western")

# Genre and Vote Average relationship
mycolors <- colorRampPalette(brewer.pal(9, "RdPu"))
ggplot() +
  geom_boxplot(data = action_vote_average, aes(x = Action, y = vote_average, color = Action)) +
  geom_boxplot(data = adventure_vote_average, aes(x = Adventure, y = vote_average, color = Adventure)) +
  geom_boxplot(data = animation_vote_average, aes(x = Animation, y = vote_average, color = Animation)) +
  geom_boxplot(data = comedy_vote_average, aes(x = Comedy, y = vote_average, color = Comedy)) +
  geom_boxplot(data = crime_vote_average, aes(x = Crime, y = vote_average, color = Crime)) +
  geom_boxplot(data = drama_vote_average, aes(x = Drama, y = vote_average, color = Drama)) +
  geom_boxplot(data = family_vote_average, aes(x = Family, y = vote_average, color = Family)) +
  geom_boxplot(data = fantasy_vote_average, aes(x = Fantasy, y = vote_average, color = Fantasy)) +
  geom_boxplot(data = mystery_vote_average, aes(x = Mystery, y = vote_average, color = Mystery)) +
  geom_boxplot(data = sciencefiction_vote_average, aes(x = `Science Fiction`, y = vote_average, color = `Science Fiction`)) +
  geom_boxplot(data = tvmovie_vote_average, aes(x = `TV Movie`, y = vote_average, color = `TV Movie`)) +
  geom_boxplot(data = romance_vote_average, aes(x = Romance, y = vote_average, color = Romance)) +
  geom_boxplot(data = thriller_vote_average, aes(x = Thriller, y = vote_average, color = Thriller)) +
  geom_boxplot(data = war_vote_average, aes(x = War, y = vote_average, color = War)) +
  geom_boxplot(data = western_vote_average, aes(x = Western, y = vote_average, color = Western)) +
  scale_fill_manual(values = mycolors) +
  labs(x = "Genres",
       y = "Vote_Average",
       title = "Vote Average Against Genres") +
  scale_colour_discrete("Genres")
```

# Correlation Plot 
```{r correlation plot}
numeric_columns <- sapply(movies, is.numeric)
movies_numeric <- movies[,numeric_columns]
correlation_of_movies <- cor(movies_numeric)
corrplot(correlation_of_movies, method = "color",col = brewer.pal(n = 10, name = 'BuPu'))
```

# Correlation Analysis 
```{r correlation analysis}
correlation_of_movies
```

# Voting average and popularity 
```{r vote popularity}
vote_popularity <- ggplot(movies, aes(vote_average, popularity)) + 
  geom_point(color = "orange") + 
  labs(x = "Vote Average",
       y = "Popularity",
       title = "Vote Average against Popularity")
vote_popularity
```

# Voting average and budget 
```{r vote budget}
vote_budget <- ggplot(movies, aes(vote_average, budget)) +
  geom_point(colour = "purple") +
  labs(x = "Vote Average",
       y = "Budget",
       title = "Vote Average against Budget")
vote_budget
```

