---
title: "Movie Madness"
author: "MaggieChen"
date: "8/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocess

```{r }
suppressMessages(library(readr))
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(tidyverse))
suppressMessages(library(stringr))
suppressMessages(library(statsr))
suppressMessages(library(gridExtra))
suppressMessages(library(corrplot))


setwd("~/STDS Assignment")
movies <- read_tsv("all_top_rated_movies_2021-08-28.tsv.txt")
movies_new <- read_tsv("all_top_rated_movies_2021-09-01.tsv.txt")

glimpse(movies_new)

colSums(is.na(movies_new)) #check the missing values

```



## Correlation among variables

From the correlation chart, it can observe that vote_count has positively correlated with revenue and budget. It may assume that higher budget and revenue movie has higher attention from the audiences, earning more votes.

```{r}
vars <- names(movies_new) %in% c('runtime', 'popularity', 'vote_average', 'budget','revenue','vote_count')
selected_train <- movies_new[vars]
corr.matrix <- cor(selected_train)
corrplot(corr.matrix, main="\n\nCorrelation Plot of numerical variables", method="number")

```


##Regression

### Regression of popularity and movie rating

The plot shows a clear trend of higher rating when popularity is higher. That means when the casts of the movie or the movie itself are popular on TMDB, the movie will also be more popular in general among audience.

From regression model, it shows that there is close to 82% of variance in movie rating that can be explained by the popularity of movies. Popularity is statistically significant predictor for the vote_average.

```{r}

# See if popularity is highly associated with rating
ggplot(data = movies_new, aes(x = popularity, y = vote_average)) +
 geom_jitter() +
 ggtitle("Plot of movie popularity vs rating") +
 geom_smooth(method = "lm")

m_popularity <- lm(vote_average ~ popularity, data = movies_new)
summary(m_popularity)

```

### Regression of movie budget and revenue

The plot shows a clear positive relationship between budget and revenue. 

```{r}

ggplot(data = movies_new, aes(x =budget , y = revenue)) +
 geom_jitter() +
 ggtitle("Plot of movie budget vs revenue") +
 geom_smooth(method = "lm")

```

## Modelling
###Dependent variable: vote_average

The model indicates that there is close to 74% of variance on movie rating that can be explained by the independent variables. All the variables have positive correlation with rating, while budget seems to have negative correlation with movie rating. It depicts that even though a movie has a higher budget, it does not mean that it will be successful.

```{r}
full_model <- lm(vote_average~revenue+popularity+budget+vote_count+runtime, data=movies_new)
summary(full_model)

```

###Dependent variable: popularity

From the model, it demonstrates that there is 94% of variance of popularity can be explained by other 5 independent variables. There's an interesting fact that shorter the movie length (runtime), the more popular the movie is among audiences.

```{r}
t_model <- lm(popularity~vote_average+revenue+popularity+budget+vote_count+runtime, data=movies_new)
summary(t_model)
```

